\Title

### 2021-01-27 manuscript/manuscript.tex

The results of our tests on synthetic data
(Figs~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences}) show that there are no significant
differences between source distribution strategies, both in terms of the
interpolation RMS errors and from visual inspection of the difference maps.
Therefore, we argue that all source distribution strategies are able to produce
comparably accurate interpolations.
Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
sources to when compared with other strategies, which reduces the computational
load of estimating the sources coefficients and forward modelling.
To ensure that the interpolation is able to reproduce the high frequencies in
the data, the block size used in the averaging should be chosen to match the
desired grid resolution.

The choice of source depth strategy does not appear to impact the interpolation
RMS error.
At a first glance, the choice of a depth strategy also would not seem to impact
the computation time.
However, when searching for the set of hyper-parameters that produce the most
accurate interpolation (e.g., through cross-validation), one must solve the
inverse problem once for every possible combination of parameters.
A depth strategy like the \emph{variable depth} requires a higher number of
hyper-parameters (depth shift $\Delta z$, depth factor $\alpha$, and the number
of nearest neighbours $k$ from Eq.~\ref{eq:variable_depth}) than other
strategies which only require a single parameter.
Having more parameters means increasing the dimensions of the parameter space
and thus increasing the number of possible combinations.
Thus, we recommend using a \emph{constant depth} or a \emph{relative depth}
when processing large datasets in order to minimize computation time.

>>>>

The results of our tests on synthetic data
(Figs~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences}) show that there are no significant
differences between source distribution strategies, both in terms of the
interpolation RMS errors and from visual inspection of the difference maps.
Therefore, we argue that all source distribution strategies are able to produce
comparably accurate interpolations.
Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
sources when compared with other strategies, which reduces the computational
load of estimating the sources coefficients and forward modelling.
To ensure that the interpolation is able to reproduce the high frequencies in
the data, the block size used in the averaging should be chosen to match the
desired grid resolution.

The choice of source depth strategy does not appear to significantly impact the
interpolation RMS error.
In the particular case of a sparse ground survey with block-averaged-sources,
the use of a variable depth visibly reduced edge effects and artifacts in areas
of poor data coverage.
At a first glance, the choice of a depth strategy would not seem to impact
the computation time.
However, when searching for the set of hyper-parameters that produce the most
accurate interpolation (e.g., through cross-validation), one must solve the
inverse problem once for every possible combination of parameters.
A depth strategy like the \emph{variable depth} requires a higher number of
hyper-parameters (depth shift $\Delta z$, depth factor $\alpha$, and the number
of nearest neighbours $k$ from Eq.~\ref{eq:variable_depth}) than other
strategies which only require a single parameter.
Having more parameters means increasing the dimensions of the parameter space
and thus increasing the number of possible combinations.
Thus, we recommend using a \emph{constant depth} or a \emph{relative depth}
when processing large datasets in order to minimize computation time.
